\documentclass[11pt,a4paper]{article}

\usepackage[margin=2.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{booktabs}
\usepackage{array}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}

\definecolor{fvcblue}{RGB}{106,112,228}

\hypersetup{colorlinks=true,linkcolor=fvcblue,urlcolor=fvcblue,
  pdftitle={FVC Token Sale — Terms and Conditions}}

\titleformat{\section}{\bfseries}{}{0em}{}[\vspace{-4pt}\rule{\linewidth}{0.4pt}]
\titlespacing{\section}{0pt}{14pt}{6pt}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small First Venture Capital — FVC Token Sale Terms}
\fancyhead[R]{\small Confidential}
\fancyfoot[C]{\small Page \thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

\setlist{itemsep=2pt,topsep=4pt,leftmargin=1.5em}

\begin{document}

% ── HEADER ──────────────────────────────────────────────────────────────────
\begin{center}
  {\LARGE\bfseries\color{fvcblue} First Venture Capital}\\[0.4em]
  {\large\bfseries FVC Token Sale — Terms and Conditions}\\[0.3em]
  {\small Version 1.0 \quad|\quad Effective \today}
\end{center}
\vspace{0.5em}
\noindent\rule{\linewidth}{1pt}
\vspace{0.5em}

\noindent\textbf{IMPORTANT.} These Terms and Conditions (\textbf{"Terms"}) govern participation in the FVC Token Sale operated by First Venture Capital (\textbf{"Company"}). By purchasing FVC Tokens you confirm you have read, understood, and agree to be bound by these Terms. If you do not agree, do not participate.

% ── 1 ───────────────────────────────────────────────────────────────────────
\section{The Token}

FVC (\textbf{"FVC Token"}) is an ERC-20 utility token issued on the Ethereum blockchain. It does not represent equity, ownership, dividends, or any financial instrument in the Company or any affiliated entity. Purchase of FVC Tokens is not an investment in a security.

% ── 2 ───────────────────────────────────────────────────────────────────────
\section{Sale Terms}

\begin{itemize}
  \item \textbf{Price:} \$0.03 USD per FVC Token (seed round rate).
  \item \textbf{Accepted payment:} ETH and USDC/USDT on Ethereum mainnet.
  \item \textbf{ETH pricing:} Converted at the Chainlink ETH/USD spot rate at the time of transaction.
  \item \textbf{Total supply cap:} 1,000,000,000 FVC.
  \item \textbf{All sales are final.} No refunds once a transaction is confirmed on-chain.
\end{itemize}

% ── 3 ───────────────────────────────────────────────────────────────────────
\section{Vesting}

All tokens purchased in this Sale are subject to the following vesting schedule, enforced by audited smart contract:

\vspace{0.5em}
\begin{center}
\begin{tabular}{>{\bfseries}l l}
\toprule
Cliff & 12 months from purchase date \\
Total duration & 24 months from purchase date \\
Release type & Linear, commencing after cliff \\
Claim & Manual — Purchaser must call \texttt{release()} \\
\bottomrule
\end{tabular}
\end{center}
\vspace{0.5em}

Tokens are held in the Vesting Smart Contract during the lock period and are not visible in the Purchaser's wallet until claimed. Vesting schedules can be viewed at \href{https://fvcdigital.com/buy-fvc}{fvcdigital.com/buy-fvc}.

% ── 4 ───────────────────────────────────────────────────────────────────────
\section{Eligibility}

Participation is restricted to persons who: (a) are 18 or older; (b) are not resident in any jurisdiction where participation is prohibited (including the USA and PRC); (c) have passed KYC/AML verification where required; and (d) understand the risks of digital assets.

% ── 5 ───────────────────────────────────────────────────────────────────────
\section{Risks}

The Purchaser acknowledges: token value may fall to zero; no liquid market is guaranteed; regulatory changes may restrict transferability; smart contracts may contain undiscovered vulnerabilities despite audit; loss of private keys results in permanent loss of tokens.

% ── 6 ───────────────────────────────────────────────────────────────────────
\section{Limitation of Liability}

To the maximum extent permitted by law, the Company's total liability to any Purchaser shall not exceed the amount paid by that Purchaser. The Company is not liable for indirect, consequential, or punitive damages, or for losses arising from private key compromise, market movements, or regulatory changes.

% ── 7 ───────────────────────────────────────────────────────────────────────
\section{Governing Law}

These Terms are governed by the laws of England and Wales. Disputes shall be subject to the exclusive jurisdiction of the courts of England and Wales.

% ── SIGNATURE ───────────────────────────────────────────────────────────────
\vspace{2em}
\noindent\rule{\linewidth}{0.4pt}

\vspace{2em}
\begin{tabular}{p{7cm} p{1cm} p{7cm}}
\cline{1-1}\cline{3-3}\\
\textbf{Purchaser Signature} && \textbf{Date}\\[2.5em]
\cline{1-1}\cline{3-3}\\
\textbf{Purchaser Full Name} && \textbf{Wallet Address}\\[2.5em]
\cline{1-1}\cline{3-3}\\
\textbf{For First Venture Capital} && \textbf{Date}\\
\end{tabular}

\vspace{2em}
\begin{center}
{\small\color{gray} First Venture Capital $\cdot$ \href{https://fvcdigital.com}{fvcdigital.com} $\cdot$ v1.0 $\cdot$ \today}
\end{center}

\end{document}
